%-----------EDUCATION-----------%
\section{Education}
    \resumeSubHeadingListStart

\resumeSubheading
    {Minerva University}{San Francisco, CA}
    {Bachelor of Arts BA, Computer Science \& Cognitive Science} 
    {}
    \resumeItemListStart
         \resumeItem{\textbf{GPA: }4.0/4.0}
        \resumeItem{\textbf{Relevant Coursework:} Modern Economic Thought, Single and Multivariate Calculus, Linear Algebra, Data Structures and Algorithms, Complex Systems, Formal Analysis, Empirical Analysis}
         \resumeItem{\textbf{Awards:}   180 DC Fellow, AI Consensus fellow }
     
    \resumeItemListEnd
      \resumeSubheading
    {Pearson College UWC}{Victoria, BC}
    {International Baccalaureate}  
{At Pearson College UWC, one of 18 United World Colleges worldwide, I thrived in a community of students from over 100 countries while pursuing the IB Diploma on a full scholarship through the Grant MacEwan Award, Canada’s largest undergraduate scholarship.

I made a lasting impact through leadership, sustainability, and innovation. I revitalized Le Dép, the student-run campus store, and ran Chic Boutique, the campus thrift store, both of which funded initiatives like free menstrual products and arts programs. I also led the sewing room and sustainable fashion program, promoting creative reuse and environmental awareness.

I founded and led Pearson’s robotics team, combining my passion for STEM and collaboration. As a language buddy, I tutored peers in English, supporting international students in adapting to an English-speaking academic environment. Academically, I ranked in the top 5% of IB students globally.

Within student leadership, I served as a House Representative, Health and Wellness Assembly Representative, APAC Leader and Creative Director, and Student Representative for the Council of International Schools. Across all these roles, I focused on building community, supporting student wellbeing, and advancing sustainability through technology and creativity.}
    \resumeSubHeadingListEnd
